\instruct{
\begin{itemize}
% \item This homework must be done in groups of 2 and submitted to Gradescope.
% Only one of the teammates should submit the report but make sure to write the name of both team members on top of your report. Also make sure that both team members are on the submission on Gradescope.
\item \enfr{This homework must be done and submitted to Gradescope individually (you will not be collaborating with other students)}{Ce devoir doit être fait et envoyé sur Gradescope individuellement (pas de collaboration avec d'autres étudiants)}

\item \enfr{The theoretical part should be submitted as a pdf file.
It should preferably be done in \LaTeX{} by copying this project (\texttt{Menu -> Copy Project}) and working off of this exact file.
Still all \textbf{legible} solutions submitted as a pdf will be accepted.
We reserve the right to penalize  solutions that are very hard to read, even if they are correct.}{La partie théorique doit être envoyée au format pdf. Il est recommandé de l'écrire en \LaTeX{}, en clônant le répertoire (\texttt{Menu -> Copy Project}) et en travaillant directement sur ce fichier. Toutefois, toute solution \textbf{lisible} au format pdf sera acceptée. Les solutions difficiles à lire pourront être pénalisées, même si elles sont justes}

\item \enfr{The practical part should be coded in python (you can use the numpy and matplotlib libraries) and all code will be submitted as a python file to Gradescope. To enable automated code grading you should work off of the template file given in this homework folder. Do not modify the name of the file or any of the function signatures of the template file or the code grading will not work for you. You may, of course, add new functions and any regular python imports}{La partie pratique doit être codée en python (avec les librairies numpy et matplotlib), et envoyée sur Gradescope sous fichier python. Pour permettre l'évaluation automatique, vous devez travailler directement sur le modèle donné dans le répertoire de ce devoir. Ne modifiez pas le nom du fichier ou aucune des fonctions signatures, sinon l'évaluation automatique ne fonctionnera pas. Vous pouvez bien sur ajouter de nouvelles fonctions et importations python}

\item \enfr{The practical report (graphing, charts, or other report parts) should be submitted in a pdf to Gradescope.
For the report it is recommended to use a Jupyter notebook, writing math with MathJax and export as pdf.
You may alternatively write your report in \LaTeX{}; \LyX{}; Word.
In any case, you should export your report to a pdf file that you will submit.
You are of course encouraged to draw inspiration from what was done in lab sessions}{Les figures, courbes et parties pratiques du rapport doivent être envoyées au format pdf sur Gradescope. Pour le rapport il est recommandé d'utiliser un Jupyter notebook, en écrivant les formules mathématiques avec MathJax et en exportant vers pdf. Vous pouvez aussi écrire votre rapport en \LaTeX{}; \LyX{}; Word. Dans tout les cas, exportez votre rapport vers un fichier pdf que vous enverrez. Vous êtes bien sur encouragés à vous inspirer de ce qui a été fait en TP.}

\item \enfr{NOTE: Many of the math questions can be answered by using online resources and automatic math solvers.
This is perfectly fine if it helps you practice, but keep in mind that during the in-class exams you will not have access to those resources and automatic solvers}{NOTE : Beaucoup des questions mathématiques peuvent être résolues en utilisant des ressources en ligne ou des solveurs automatiques. Ce n'est pas un problème si cela vous aide à progresser, mais gardez à l'esprit que pendant les examens en classe vous n'aurez pas accès à ces ressources et solveurs. }
\end{itemize}
}